---
title: MRP analysis at LA level with Natsal3 data
output: word_document
author: N Green
editor_options: 
  chunk_output_type: console
---


```{r preamble}
library(lme4)
library(car)
library(arm)
library(pander)
library(knitr)
library(stargazer)
library(xtable)
library(lattice)
library(plyr)
library(blme)
# library(reshape)
library(reshape2)
library(optimx)

library(STIecoPredict)
```

```{r}
load("C:/Users/ngreen1/Dropbox/small_area_chlamydia/R_code/scripts/mrp/data/cleaned-regn-input-mrpNatsal.RData")

Natsal0 <- Natsal
```

```{r}
savedata <- FALSE
showplot <- TRUE
```

```{r Natsal-subsets}
## older ages sparsely sampled
Natsal <- subset(Natsal, age > 15 & age < 25)   #NCSP range

## opposite sex partner in last year only
Natsal <- subset(Natsal, sam1yr == 0)

Natsal$sex1yr <- (Natsal$het1yr != 0 | Natsal$sam1yr != 0)

Natsal$GUMvenue <- (Natsal$chtstwh1 == "Sexual health clinic (GUM clinic)" | Natsal$chltstwh == "Sexual health clinic (GUM clinic)")

## subset GUM or non-GUM only
# Natsal2 <- subset(Natsal, (GUMvenue  & cttestly==TRUE) | cttestly==FALSE)
# Natsal2 <- subset(Natsal, (!GUMvenue & cttestly==TRUE) | cttestly==FALSE)

# names.atleast1test <- rownames(table(Natsal$laname, Natsal$cttestly))[table(Natsal$laname, Natsal$cttestly)[,"1"]>0]
# names.LAbigenough <- names(table(Natsal$laname)[(table(Natsal$laname))>10])
# 
# subnames <- names.LAbigenough[names.LAbigenough%in%names.atleast1test]
# Natsal2  <- subset(Natsal, laname%in%subnames)
Natsal2 <- Natsal
```

```{r glmer-model-logistic, eval=FALSE}
fit <- lme4::glmer(
    formula = cttestly ~ 1 + sex + (1|sex.age) + (1|ethnic2) + I(hhsize == 1) + student +
                       (1|Conception.decile) +  (1|`Numerical classification`) + I(`Average Score` > 28) +
                        (1|laname) + (1|gor) + (1|metcounty_UA), # + I(gor==9) ,
    family = binomial(link = "logit"),
    data = Natsal2)
```

```{r bglmer-model-logistic, eval=TRUE}
## >28 is 75% IMD quantile
fit <- blme::bglmer(
    formula = cttestly ~ 1 + sex + (1|sex.age) + (1|ethnic2) + student + I(hhsize == 1) + (1|Conception.decile) +
                        (1|`Numerical classification`) + (1|laname) + (1|gor) + I(`Average Score` > 28) + (1|metcounty_UA), # + I(gor==9) ,
    maxit = 10000L,
    
    # control = glmerControl(optimizer = "bobyqa"),
    control = lme4::glmerControl(optimizer = "Nelder_Mead"),
    # control = glmerControl(optimizer = "optimx", optCtrl=list(method = "nlminb"),
    # control = glmerControl(optimizer = "optimx", optCtrl=list(method = "L-BFGS-B"),
    
    family = binomial(link = "logit"),
    data = Natsal2)
```


```{r tornado plots, eval=showplot}
lattice::dotplot(ranef(fit, condVar = TRUE),
                 scales = list(cex = 0.5))
```

```{r fix effect odds-ratios}
# http://www.ats.ucla.edu/stat/r/dae/melogit.htm

exp(coef(fit)$laname["YORK", ])
# exp(confint(fit))

se <- sqrt(diag(vcov(fit)))

# table of estimates with 95% CI
tab <- cbind(Est = fixef(fit),
             LL = fixef(fit) - 1.96 * se,
             UL = fixef(fit) + 1.96 * se)
tab
exp(tab)
```


```{r survey-package, eval=FALSE}
##TODO:
library(survey)

natsal3 <- svydesign(id = ~ 1,
                     weights = ~ total_wt,
                     strata = ~ strata,
                     data = Natsal0,
                     nest = TRUE)

svyglm(cttestly ~ dage + rsex + ethnic2 + student + `Numerical classification`,
       family = quasibinomial,
       design = natsal3)
```

```{r main-model-additive, eval=FALSE}
# file:///C:/Users/nathan.green.PHE/Downloads/Fitting_Additive_Binomial_Regression_Models_with_the_R_Package_blm.pdf
## is it that we can't have random effects in this model??

library(blm)

## >28 is 75% quantile
fit.blm <- blm(formula = cttestly ~ 1 + student + sex*age + laname,# + ethnic2
               weights = Natsal2$total_wt.int,
               data = Natsal2)
                    # data = Natsal)
coef(fit.blm)
```

```{r general additive model, eval=FALSE}
##TODO##
## how do I do this with categorical data??
library(gam)

# http://web.stanford.edu/~hastie/Papers/gam.pdf
fit.gam <- gam(cttestly ~ s(student) + s(sex) + s(age),
               data = Natsal2)
```

```{r residual_plot, eval=showplot}
predicted <- predict(fit, Natsal2[,c("student","sex","age","ethnic2","laname","gor","sin2")]) > 0.5

plot(predicted - Natsal2$cttestly)

table(predicted, Natsal2$cttestly)
```


### Missing LA Random Effects and Neighbour Smoothing

Because some of the LAs don't have any sample point we create a vector of LA random effects that includes these.
We set the RE to 0.


```{r missing_LA eval=TRUE}
## add some missing random effects
missingLANatsal.names <- unique(Natsal0$laname)[!unique(Natsal0$laname) %in% rownames(ranef(fit)$laname)]
missingLAsim_prop.names <- unique(sim_prop_la$LAname)[!unique(sim_prop_la$LAname) %in% rownames(ranef(fit)$laname)]
missingLA.names <- union(missingLAsim_prop.names, missingLANatsal.names)

la.ranefs <- array(0, dim = c(length(missingLA.names), 1))
dimnames(la.ranefs) <- list(missingLA.names, "(Intercept)")
la.ranefs <- rbind(ranef(fit)$laname, la.ranefs)
```

```{r missing_metUA eval=TRUE}
## add some missing random effects
missingmetUANatsal.names <- unique(Natsal0$metcounty_UA)[!unique(Natsal0$metcounty_UA) %in% rownames(ranef(fit)$metcounty_UA)]
missingmetUAsim_prop.names <- unique(sim_prop_la$metcounty_UA)[!unique(sim_prop_la$metcounty_UA) %in% rownames(ranef(fit)$metcounty_UA)]
missingmetUA.names <- na.omit(union(missingmetUAsim_prop.names, missingmetUANatsal.names))

metUA.ranefs <- array(0, dim = c(length(missingmetUA.names), 1))
dimnames(metUA.ranefs) <- list(missingmetUA.names, "(Intercept)")
metUA.ranefs <- rbind(ranef(fit)$metcounty_UA, metUA.ranefs)
```

```{r missing_gor eval=FALSE}
##TODO##
## add some missing random effects
missinggorNatsal.names <- unique(Natsal0$gor)[!unique(Natsal0$gor) %in% rownames(ranef(fit)$gor)]
missinggorsim_prop.names <- unique(sim_prop_la$gor)[!unique(sim_prop_la$gor) %in% rownames(ranef(fit)$gor)]
missinggor.names <- union(missinggorsim_prop.names, missinggorNatsal.names)

gor.ranefs <- array(0, dim = c(length(missinggor.names), 1))
dimnames(gor.ranefs) <- list(missinggor.names, "(Intercept)")
gor.ranefs <- rbind(ranef(fit)$gor, gor.ranefs)
```

Alternatively, we can take averages of the neighbouring LAs.
We can just do this for missing LA random effects or we can do this will all of the random effects.
This may help to account for the test lab mis-specification by postcode and the movement of people to test somewhere other than where they live.


```{r smoothed-missing-LAs-ranef, eval=TRUE}
## fitted LAs
LAnames <- rownames(ranef(fit)$laname)
numNeighbours <- rowSums(madjacency[ ,-1])
colnames(madjacency) <- STIecoPredict::LAnameClean(colnames(madjacency))

madjacencyRE <- madjacency

for (i in LAnames) {
    madjacencyRE[, i] <- madjacencyRE[, i]*ranef(fit)$laname[i, ]
}

madjacencyRE[madjacencyRE == 1] <- 0

rowAverages <- array(rowSums(madjacencyRE[ ,-1])/numNeighbours, dim = c(length(numNeighbours), 1))
rowAverages[is.nan(rowAverages)] <- 0
dimnames(rowAverages) <- list(madjacencyRE[ ,1], "(Intercept)")

missingLANatsal.names <- unique(Natsal0$laname)[!unique(Natsal0$laname) %in% rownames(ranef(fit)$laname)]
missingLAsim_prop.names <- unique(sim_prop_la$LAname)[!unique(sim_prop_la$LAname) %in% rownames(ranef(fit)$laname)]
missingLA.names <- union(missingLAsim_prop.names, missingLANatsal.names)

la.ranefs <- subset(rowAverages, rownames(rowAverages) %in% missingLA.names)
la.ranefs <- rbind(ranef(fit)$laname, la.ranefs)
```

```{r smoothed--all--LAs-ranef, eval=FALSE}
## takes mean average of each LA and its neighbours

names(madjacency) <- LAnameClean(names(madjacency))
madjacency[ ,1] <- LAnameClean(madjacency[, 1])

## fitted LAs
LAnames <- rownames(ranef(fit.cttestly)$laname)

madjacencyRE <- madjacency

# madjacencyRE <- madjacencyRE[, c(TRUE,(names(madjacency)%in%LAnames)[-1])]  #not missing LAs
# madjacencyRE <- madjacencyRE[(names(madjacency)%in%LAnames)[-1],]

for (i in 1:nrow(madjacencyRE)) madjacencyRE[i, i + 1] <- 1   #diagonal (not including first column)

# numNeighbours <- rowSums(madjacencyRE[, -1])  #true number of neigbours

## fillin fitted random effects
for (i in LAnames){
    madjacencyRE[, i] <- madjacencyRE[, i] * ranef(fit)$laname[i, ]
}

madjacencyRE[madjacencyRE == 1] <- 0    #if don't have fitted RE then remove from average

## number of neighbours with values
numNeighbours <- apply(madjacencyRE[ ,-1], 1, function(x) sum(x != 0)) #numNeighbours <- rowSums(madjacencyRE[, -1])

rowAverages <- array(rowSums(madjacencyRE[ ,-1])/numNeighbours, dim = c(length(numNeighbours),1))
rowAverages[is.nan(rowAverages)] <- 0
dimnames(rowAverages) <- list(madjacencyRE[ ,1], "(Intercept)")

## who is still without an estimate?
missingLANatsal.names <- unique(Natsal0$laname)[!unique(Natsal0$laname) %in% rownames(rowAverages)]
missingLAsim_prop.names <- unique(sim_prop_la$LAname)[!unique(sim_prop_la$LAname) %in% rownames(rowAverages)]
missingLA.names <- union(missingLAsim_prop.names, missingLANatsal.names)

la.ranefs <- array(0, dim = c(length(missingLA.names), 1))
dimnames(la.ranefs) <- list(missingLA.names, "(Intercept)")
la.ranefs <- rbind(rowAverages, la.ranefs)
```



## Try different ethnic group probabilities

```{r try-different-pethnic2, eval=FALSE}
# LA_ethnic2 <- melt(LA_ethnic2, id.vars = "LA Name", variable.name = "ethnic2")
# LA_ethnic2$`LA Name` <- LAnameClean(LA_ethnic2$`LA Name`)
# LA_ethnic2$`LA Name` <- toupper(LA_ethnic2$`LA Name`)
# LA_ethnic2$ethnic2 <- toupper(LA_ethnic2$ethnic2)
# LA_ethnic2$value <- LA_ethnic2$value/100
# names(LA_ethnic2)[names(LA_ethnic2)=="value"] <- "p.ethnic2"

#ONS via guardian website
LA_ethnic2 = get("LA_ethnic2", asNamespace('STIecoPredict'))

sim_prop_la <- sim_prop_la[ ,names(sim_prop_la) != "p.ethnic2"]
sim_prop_la <- merge(sim_prop_la, LA_ethnic2, by = c("LAname", "ethnic2"), all.x=TRUE)
```


### This are the main MRP steps

# Append predictions to joint distribution dataset

```{r classif_probs}
fixeff.formula <- as.formula("cttestly ~ student + sex + age + ethnic2 + livealone")

## census data
# test.calcTotalProbs(sim_prop_la)
sim_prop_la.fit <- STIecoPredict:::calcTotalProbs(formula = fixeff.formula,
                                                  data = sim_prop_la,
                                                  extracols = c("LAname","gor","Average Score","metcounty_UA","Numerical classification","Conception.deciles"))

pred <- arm::invlogit(
                    fixef(fit)["(Intercept)"] +
                     
                    fixef(fit)["sexWomen"]*(sim_prop_la.fit$sex == "Women") +
                 
                    fixef(fit)["studentTRUE"]*(sim_prop_la.fit$student) +
                        
                    fixef(fit)["I(hhsize == 1)TRUE"]*(sim_prop_la.fit$livealone) +
                 
                    ranef(fit)$ethnic2[as.character(sim_prop_la.fit$ethnic2), 1] +

                    ##ranef(fit)$age[as.character(sim_prop_la.fit$age),1] +
                      
                    ranef(fit)$'sex.age'[paste(sim_prop_la.fit$sex, sim_prop_la.fit$age, sep = "."), 1] +
                        
                    ## ranef(fit)$laname[as.character(sim_prop_la.fit$LAname),1] +
                    la.ranefs[as.character(sim_prop_la.fit$LAname), 1] +
                        
                    ranef(fit)$gor[as.character(sim_prop_la.fit$gor), 1] +
                    ## fixef(fit)["I(gor == 9)TRUE"]*(sim_prop_la.fit$gor == 9)    #london
                        
                    ## ranef(fit)$metcounty_UA[as.character(sim_prop_la.fit$metcounty_UA), 1] #+
                    metUA.ranefs[as.character(sim_prop_la.fit$metcounty_UA), 1] +
                    
                    fixef(fit)["I(`Average Score` > 28)TRUE"]*(sim_prop_la.fit$`Average Score` > 28) +
                      
                    ranef(fit)$`Numerical classification`[as.character(sim_prop_la.fit$`Numerical classification`), 1] +
                        
                    ranef(fit)$Conception.decile[as.character(sim_prop_la.fit$Conception.deciles), 1]
)
```

```{r weight_and_sum}
## weight the probabilities by the subpopulation sizes and then sum by LA

predweighted <- pred * sim_prop_la.fit$totalprob

LApred <- tapply(predweighted, sim_prop_la.fit$LAname, sum)
```

The LA specific post-stratified estimates are then

```{r LA_predictions}
LApred <- data.frame(LApred = LApred[order(LApred)])
```


## Re-adjust for conditioning of ages between 16-24 only

What am I doing here??...

```{r LApred.adj}
# popCensus <- read.csv("..\\..\\packages\\STIecoPredict\\raw-data\\popCensus.csv")

LApred$LAname <- rownames(LApred)
popCensus$LAname <- STIecoPredict:::LAnameClean(popCensus$LAname)

rownames(LApred) <- NULL

LApred <- merge(LApred, popCensus[popCensus$Sex == "All", c("LAname","prob.25.and.over")],
                all.x = TRUE)

LApred$LApred.adj <- LApred$LApred*(1 - LApred$prob.25.and.over)

LApred[order(LApred$LApred.adj), ]
```


```{r, eval=savedata}
save(pred, LApred, file = "data/predictions.RData")
```


Calculate the output values using the raw data.

```{r direct_estimates_la}
## raw
NatsalLA <- melt(tapply(Natsal2$cttestly, Natsal2$laname, mean),
                 varnames = c("LA.Name")) #direct estimate

NatsalLAsize <- melt(tapply(Natsal2$cttestly, Natsal2$laname, length),
                     varnames = c("LA.Name"))
#as.NatsalLAsize <- data.frame(table(Natsal2$laname))

## with sample weights
NatsalLA.weights <- ddply(.data = Natsal2,
                          .variables = .(laname),
                          function(y) data.frame(wtmean = weighted.mean(x = y$cttestly,
                                                                        w = y$total_wt)))

## use predictions instead of data
##TODO##
Natsal2$cttestly.predict <- predict(fit, type = "response")
NatsalLA.predict <- melt(tapply(Natsal2$cttestly.predict,
                                Natsal2$laname, mean),
                         varnames = c("LA.Name")) #direct estimate
NatsalLA.weights.predict <- ddply(.data = Natsal2,
                                  .variables = .(laname),
                                  function(y) data.frame(wtmean = weighted.mean(x = y$cttestly.predict,
                                                                                w = y$total_wt)))
```


## Surveillance data

Combine predictions with the surveillance data and produce summary statistics for each area.

```{r all_joined_output}
CTADGUM_pred <- STIecoPredict:::joinAllOutcomeData(LApred, adj = 0.945)

CTADGUM_pred <- STIecoPredict:::calcStats.CTADGUM_pred(CTADGUM_pred)
```

```{r Natsal_surveillance_joins}
CTADGUM_pred <- merge(CTADGUM_pred, NatsalLA[ ,c("LA.Name", "value")],
                      by.x = "LA Name", by.y = "LA.Name", all.x = TRUE)

CTADGUM_pred <- merge(CTADGUM_pred, NatsalLA.weights[ ,c("laname", "wtmean")],
                      by.x = "LA Name", by.y = "laname", all.x = TRUE)

CTADGUM_pred <- merge(CTADGUM_pred, NatsalLAsize[ ,c("LA.Name", "value")],
                      by.x = "LA Name", by.y = "LA.Name", all.x = TRUE)

names(CTADGUM_pred)[names(CTADGUM_pred) %in% c("value.x", "value.y")] <- c("NatsalLA", "NatsalLAsize")

CTADGUM_pred$NatsalLAsize[is.na(CTADGUM_pred$NatsalLAsize)] <- 1.5  #missing LAs

CTADGUM_pred$`LA Name` <- as.factor(CTADGUM_pred$`LA Name`)
CTADGUM_pred$laname.num <- as.numeric(CTADGUM_pred$`LA Name`)

CTADGUM_pred$Region <- droplevels(CTADGUM_pred$Region)
CTADGUM_pred <- CTADGUM_pred[order(CTADGUM_pred$Region), ]

x <- by(CTADGUM_pred, CTADGUM_pred$Region, nrow)

CTADGUM_pred$LAnum_inregion <- unlist(sapply(x, function(z) z:1))
```


```{r eval=savedata}
save(CTADGUM_pred, file = "data/CTADGUM_pred-with-LA.RData")
```


### Include uncertainty on ethnicity probabilities
##TODO## ??

```{r eval=FALSE}

library(gtools)

temp <- dcast(data = sim_prop_la,
              formula = LAname + age + sex + smokenow + increasingdrinker + student ~ ethnic2,
              value.var = "p.ethnic2")

temp2 <- t(round(apply(temp[ ,7:12]*10, 1,
                       function(x) rdirichlet(n = 1, alpha = x)), 5))

apply(temp2, 2, median)
colnames(temp2) <- names(temp[ ,7:12])
mtemp <- data.frame(temp[ ,-(7:12)], temp2)
sample.ethnic2 <- melt(data = mtemp,
                       measure.vars = make.names(names(temp[ ,7:12])),
                       variable.name = "ethnic2")

```


