---
title: MRP script of LA-level chlaymdia coverage analysis using WinBUGS
author: N Green
date: 13-05-2016
output: word_document
---

This document takes the results of the Bayesian hierarchical model fitting using the Natsal-3 data and WinBUGS to then perform post-stratification to estimate the LA level chlamydia coverage in the previous year.

There's an equivalent script for do this with the `glmer` function for classical (non-Bayesian) regression which is much faster to fit.


```{r preamble}
library(lme4)
library(car)
library(arm)
library(pander)
library(knitr)
library(stargazer)
library(xtable)
library(lattice)
library(plyr)
library(STIecoPredict)
library(R2WinBUGS)
library(coda)

# load("C:/Users/ngreen1/Dropbox/small-area & chlamydia/R_code/scripts/mrp/data/cleaned-regn-input-mrpNatsal.RData")
load("./data/cleaned-regn-input-mrpNatsal.RData")
```

```{r load_data}
Natsal0 <- Natsal

load("../WinBUGS/WinBUGS_with-all_LA-vars/outmat.RData")

savedata <- FALSE

nsample <- nrow(outmat)
```

```{r eval=FALSE}
## raw WinBUGS output
coda1.file <- "../WinBUGS/WinBUGS_with-all_LA-vars/coda1.txt"
coda2.file <- "../WinBUGS/WinBUGS_with-all_LA-vars/coda2.txt"
coda3.file <- "../WinBUGS/WinBUGS_with-all_LA-vars/coda3.txt"
outmcmc <- read.bugs(c(coda1.file, coda2.file, coda3.file))
```


```{r posterior_summary}
posterior.summary <- as.data.frame(t(apply(outmat, 2, quantile, probs=c(0.025,0.25,0.75,0.975) )))
posterior.summary$variable <- rownames(posterior.summary)
# posterior.summary <- posterior.summary[posterior.summary$variable!="deviance",]

posterior.means <- apply(outmat, 2, mean)
names(posterior.means) <- toupper(names(outmat))
```


Because some of the LAs don't have any sample point we create a vector of LA random effects that includes these. We set these REs to 0.
Could alternatively take e.g. average of neighbours instead.

```{r fillin_missingLAs}
missingLAnames <- names(posterior.means)[!levels(sim_prop_la$LAname)%in%names(posterior.means)]
missingLAs <- rep(0,length(missingLAnames))
names(missingLAs) <- missingLAnames

#ad-hoc!
posterior.means <- c(posterior.means,
                     c("CHRISTCHURCH"=0, "MALDON"=0, "ROCHFORD"=0, "UTTLESFORD"=0, "WATFORD"=0, "RIBBLE VALLEY"=0, "RICHMONDSHIRE"=0, "CHERWELL"=0, "NORTH WARWICKSHIRE"=0))

posterior.means <- c(posterior.means, missingLAs)
posterior.means <- c(posterior.means, `15`=as.numeric(posterior.means["16"]))
```


# Append predictions to joint distribution dataset

```{r classif_probs}

fixeff.formula <- as.formula("cttestly ~ student + sex + age + ethnic2")

## census data
# test.calcTotalProbs(sim_prop_la)
sim_prop_la <- STIecoPredict:::calcTotalProbs(formula=fixeff.formula, data=sim_prop_la, extracols = c("LAname","gor"))

## select chunks appropriate for given model
pred <- arm::invlogit(
                    posterior.means["ALPHA"] +
                     
                    posterior.means["B.MALE"]*(sim_prop_la$sex=="Men") +
                 
                    posterior.means["B.STUDENT"]*(sim_prop_la$student) +
                 
                    posterior.means[as.character(sim_prop_la$ethnic2)] +

                    posterior.means[as.character(sim_prop_la$age)] +
                      
                    posterior.means[as.character(sim_prop_la$LAname)]
                   )
```

```{r weight_and_sum}
## weight the probabilities by the subpopulation sizes and then sum by LA

predweighted <- pred * sim_prop_la$totalprob
LApred <- tapply(predweighted, sim_prop_la$LAname, sum, na.rm=TRUE)
```

The LA specific post-stratified estimates are then

```{r LA_predictions}
(LApred <- data.frame(LApred=LApred[order(LApred)]))
```


## Re-adjust for conditioning of ages between 16-24 only

```{r}
# popCensus <- read.csv("..\\..\\packages\\STIecoPredict\\raw-data\\popCensus.csv")
LApred$LAname <- rownames(LApred)
popCensus$LAname <- STIecoPredict:::LAnameClean(popCensus$LAname)
rownames(LApred) <- NULL
LApred <- merge(LApred, popCensus[popCensus$Sex=="All", c("LAname","prob.25.and.over")], all.x=TRUE)
LApred$LApred.adj <- LApred$LApred*(1-LApred$prob.25.and.over)
```


```{r, eval=savedata}
save(pred, LApred, file="data/predictions.RData")
```

```{r direct_estimates_la}
library(reshape2)
agerange <- 15:24
NatsalLA <- melt(tapply(Natsal$cttestly[Natsal$age%in%agerange], Natsal$laname[Natsal$age%in%agerange], mean), varnames = c("LA Name"))
NatsalLAsize <- melt(tapply(Natsal$cttestly[Natsal$age%in%agerange], Natsal$laname[Natsal$age%in%agerange], length), varnames = c("LA Name"))
```


## Surveillance data

Combine predictions with the surveillance data and produce summary statistics for each area.

```{r all_joined_output}
CTADGUM_pred <- STIecoPredict:::joinAllOutcomeData(pred=LApred)
CTADGUM_pred <- STIecoPredict:::calcStats.CTADGUM_pred(CTADGUM_pred)
```

```{r eval=savedata}
save(CTADGUM_pred, file="data/CTADGUM_pred.RData")
```

```{r Natsal_surveillance_joins}
CTADGUM_pred <- merge(CTADGUM_pred, NatsalLA[,c("LA Name", "value")], by="LA Name", all.x=TRUE)
CTADGUM_pred <- merge(CTADGUM_pred, NatsalLAsize[,c("LA Name", "value")], by="LA Name", all.x=TRUE)
names(CTADGUM_pred)[names(CTADGUM_pred)%in%c("value.x", "value.y")] <- c("NatsalLA", "NatsalLAsize")
```


### Propogate the posterior uncertainty

```{r fillin_missingLAs}
missingLAs <- as.data.frame(matrix(0, nrow = nsample, ncol = length(missingLAnames)))
names(missingLAs) <- missingLAnames
outmat <- cbind(outmat, missingLAs)

#ad-hoc!
outmat <- data.frame(outmat,
            cbind("CHRISTCHURCH"=rep(0,nsample), "MALDON"=rep(0,nsample), "ROCHFORD"=rep(0,nsample), "UTTLESFORD"=rep(0,nsample), "WATFORD"=rep(0,nsample), "RIBBLE VALLEY"=rep(0,nsample), "RICHMONDSHIRE"=rep(0,nsample), "CHERWELL"=rep(0,nsample), "NORTH WARWICKSHIRE"=rep(0,nsample)), check.names = FALSE)

names(outmat) <- toupper(names(outmat))
predmat <- matrix(NA, ncol = nsample, nrow = nrow(sim_prop_la))
```


```{r classif_probs_vector, eval=FALSE}
for (i in 1:nsample){
  
predmat[i,] <- arm::invlogit(
                    outmat[i,"ALPHA"] +
                     
                    outmat[i, "B.MALE"]*(sim_prop_la$sex=="Men") +
                 
                    outmat[i, "B.STUDENT"]*(sim_prop_la$student) +
                 
                    outmat[i, as.character(sim_prop_la$ethnic2)] +

                    outmat[i, as.character(sim_prop_la$age)] +
                      
                    outmat[i, as.character(sim_prop_la$LAname)]
                   )
}
```


```{r classif_probs_datatables, eval=TRUE}
library(data.table)

outmelt <- melt(data.frame(sample=1:nsample,outmat), id.vars="sample")
DT <- data.table(outmelt)
setkeyv(DT, cols=c("sample","variable"))

#<3 mins
#covariates x sample
for (i in 1:nsample){
  
predmat[,i] <- arm::invlogit(
  
  DT[list(i,"ALPHA")]$value +
  DT[list(i,"B.MALE")]$value *(sim_prop_la$sex=="Men") +
  DT[list(i,"B.STUDENT")]$value *(sim_prop_la$student) +
    
  DT[list(i, make.names(sim_prop_la$ethnic2))]$value +
  DT[list(i, make.names(sim_prop_la$age))]$value +
  DT[list(i, make.names(sim_prop_la$LAname))]$value)
}

save(predmat, file="all_combinations_posterior_sample.RData")
```


```{r}
## weight the probabilities by the subpopulation sizes and then sum by LA

predweighted <- sweep(predmat, MARGIN=1, sim_prop_la$totalprob, `*`)
LApred <- aggregate(predweighted ~ sim_prop_la$LAname, FUN = sum)
```

```{r eval=FALSE}
CTADGUM_pred <- STIecoPredict:::joinAllOutcomeData(pred=LApred)
CTADGUM_pred <- STIecoPredict:::calcStats.CTADGUM_pred(CTADGUM_pred)
```


