---
output: word_document
---


```{r preamble}
library(lme4)
library(car)
library(arm)
library(pander)
library(knitr)
library(stargazer)
library(xtable)
library(lattice)
library(plyr)

library(STIecoPredict)

# load("C:/Users/ngreen1/Dropbox/small-area & chlamydia/R_code/scripts/mrp/data/cleaned-regn-input-mrpNatsal.RData")
load("./data/cleaned-regn-input-mrpNatsal.RData")
```

```{r Natsal}
Natsal0 <- Natsal
## older ages sparsely sampled
Natsal <- subset(Natsal, age>15 & age<45)
Natsal <- subset(Natsal, age>15 & age<25)   #NCSP range

savedata <- FALSE
```


```{r main-model}
fit <- glmer(formula = cttestly ~ 1+student+smokenow+ (1|sex:age)+(1|ethnic2)+(1|gor),
              data = Natsal, family = binomial(link="logit"), weights = total_wt.int)
```


# Append predictions to joint distribution dataset

```{r classif_probs}
if(!exists(formula)){
    formula <- paste(fit@call$formula, collapse = "")
}

## convert formula to fixed effect model with same variables
TERMS <- attr(terms(fit@call$formula),"term.labels")
TERMS <- unlist(strsplit(TERMS, split=" \\| "))
TERMS <- unlist(strsplit(TERMS, split=":"))
TERMS <- gsub(" ", "", TERMS, fixed = TRUE)
TERMS <- TERMS[TERMS!="1" & TERMS!="gor"]

fixeff.formula <- as.formula(paste("cttestly~",paste(TERMS, collapse = "+"),sep=""))

## census data
# test.calcTotalProbs(sim_prop_la)
sim_prop_la <- STIecoPredict:::calcTotalProbs(formula=fixeff.formula, data=sim_prop_la, extracols = c("LAname","gor"))

## select chunks appropriate for given model
pred <- invlogit(fixef(fit)["(Intercept)"] +
                     
                     # (fixef(fit)["sexWomen"]*(sim_prop_la$sex=="Women")) +
                     (fixef(fit)["studentTRUE"]*sim_prop_la$student) +
                   
                    # if(grep("+ethnic2", formula)==1){}
                     # (fixef(fit)["studentTRUE:sexWomen"]*(sim_prop_la$sex=="Women" & sim_prop_la$student)) +
                     # (fixef(fit)["ethnic2ASIAN/ASIAN BRITISH"]*(sim_prop_la$ethnic2=="ASIAN/ASIAN BRITISH")) +
                     # (fixef(fit)["ethnic2BLACK/BLACK BRITISH"]*(sim_prop_la$ethnic2=="BLACK/BLACK BRITISH")) +
                     # (fixef(fit)["ethnic2CHINESE"]*(sim_prop_la$ethnic2=="CHINESE")) +
                     # (fixef(fit)["ethnic2MIXED"]*(sim_prop_la$ethnic2=="MIXED")) +
                     # (fixef(fit)["ethnic2OTHER"]*(sim_prop_la$ethnic2=="OTHER")) +
                     # (fixef(fit)["ethnic2NOT ANSWERED"]*(sim_prop_la$ethnic2=="NOT ANSWERED")) +
                   
                     (fixef(fit)["smokenowTRUE"]*sim_prop_la$smokenow) +
                     
                    # if(grep("+increasingdrinker", formula)==1){}                     
                     # (fixef(fit)["increasingdrinkerTRUE"]*sim_prop_la$increasingdrinker)+
                     
                   # if(grep("\\(student|age\\)", formula)==1){}
                     # (ranef(fit)$age[as.character(sim_prop_la$age),2]*sim_prop_la$student) +
                   
                   # if(grep("\\(1|ethnic2\\)", formula)==1){}
                      ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1] +
                   
                   # if(grep("\\(1|sex:age\\)", formula)==1){}
                      ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age, sep=":"), 1] +
                     
                   # if(grep("\\(increasingdrinker|ethnic2\\)", formula)==1){}
                      # ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),"(Intercept)"] +
                      # ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),2]*sim_prop_la$increasingdrinker +
    
                   # if(grep("\\(ethnic2|age\\)", formula)==1){}
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "(Intercept)"]) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2ASIAN/ASIAN BRITISH"]*(sim_prop_la$ethnic2=="ASIAN/ASIAN BRITISH")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2BLACK/BLACK BRITISH"]*(sim_prop_la$ethnic2=="BLACK/BLACK BRITISH")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2CHINESE"]*(sim_prop_la$ethnic2=="CHINESE")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2MIXED"]*(sim_prop_la$ethnic2=="MIXED")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2OTHER"]*(sim_prop_la$ethnic2=="OTHER")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2NOT ANSWERED"]*(sim_prop_la$ethnic2=="NOT ANSWERED")) +

                   # if(grep("\\(1|age\\)", formula)==1){}
                     # ranef(fit)$age[as.character(sim_prop_la$age),1] +
                 
                   # if(grep("\\(sex|age\\)", formula)==1){}
                      # ranef(fit)$age[as.character(sim_prop_la$age),"(Intercept)"] +
                      # ranef(fit)$age[as.character(sim_prop_la$age),2]*(sim_prop_la$sex=="Women") +
                     
                   # if(grep("\\(1|age.scaled\\)", formula)==1){}
                     # ranef(fit)$age.scaled[as.character(sim_prop_la$age.scaled),1] +
                   
                   # if(grep("\\(1|gor\\)", formula)==1){}
                     ranef(fit)$gor[as.character(sim_prop_la$gor),1]
                   )
```

```{r weight_and_sum}
## weight the probabilities by the subpopulation sizes and then sum by LA

predweighted <- pred * sim_prop_la$totalprob
LApred <- tapply(predweighted, sim_prop_la$LAname, sum)
```

The LA specific post-stratified estimates are then

```{r LA_predictions}
(LApred <- data.frame(LApred=LApred[order(LApred)]))
```


## Re-adjust for conditioning of ages between 16-24 only

```{r LApred.adj}
popCensus <- read.csv("..\\..\\packages\\STIecoPredict\\raw-data\\popCensus.csv")
LApred$LAname <- rownames(LApred)
popCensus$LAname <- STIecoPredict:::LAnameClean(popCensus$LAname)
rownames(LApred) <- NULL
LApred <- merge(LApred, popCensus[popCensus$Sex=="All", c("LAname","prob.25.and.over")], all.x=TRUE)
LApred$LApred.adj <- LApred$LApred*(1-LApred$prob.25.and.over)

LApred[order(LApred$LApred.adj),]
```


```{r, eval=savedata}
save(pred, LApred, file="data/predictions.RData")
```


## Surveillance data

Combine predictions with the surveillance data and produce summary statistics for each area.

```{r all_joined_output}
CTADGUM_pred <- STIecoPredict:::joinAllOutcomeData(LApred)
CTADGUM_pred <- STIecoPredict:::calcStats.CTADGUM_pred(CTADGUM_pred)
```

```{r eval=savedata}
save(CTADGUM_pred, file="data/CTADGUM_pred.RData")
```


## Some validation plots

This is taken from Gelman (xxxx).
We predict using the logistic fit without one of the covariates and then plot a separate line for each.


```{r gor_model_validation}
gor.names <- c("North East", #1
               "North West", #2
               "notused", #3
               "Yorkshire and The Humber", #4
               "East Midlands", #5
               "West Midlands", #6
               "South West", #7
               "East", #8
               "London", #9
               "South East", #10
               "Wales", #11
               "Scotland") #12

pred.logit <- (fixef(fit)["smokenowTRUE"]*sim_prop_la$smokenow) +
               fixef(fit)["studentTRUE"]*sim_prop_la$student +
               ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1] +
               ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age,sep=":"), 1]

pred.logit.Natsal <- (fixef(fit)["smokenowTRUE"]*Natsal$smokenow) +
                        fixef(fit)["studentTRUE"]*Natsal$student +
                        ranef(fit)$ethnic2[as.character(Natsal$ethnic2),1] +
                        ranef(fit)$'sex:age'[paste(Natsal$sex, Natsal$age,sep=":"), 1]

pred.logit.upperCI <- ((fixef(fit)["smokenowTRUE"]+2*se.fixef(fit)["smokenowTRUE"])*sim_prop_la$smokenow) +
                       (fixef(fit)["studentTRUE"]+2*se.fixef(fit)["studentTRUE"])*sim_prop_la$student +
                       (ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1]+2*se.ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1]) +
                       (ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age,sep=":"), 1]+2*se.ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age,sep=":"), 1])

pred.logit.lowerCI <- ((fixef(fit)["smokenowTRUE"]-2*se.fixef(fit)["smokenowTRUE"])*sim_prop_la$smokenow) +
                       (fixef(fit)["studentTRUE"]-2*se.fixef(fit)["studentTRUE"])*sim_prop_la$student +
                       (ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1]-2*se.ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1]) +
                       (ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age,sep=":"), 1]-2*se.ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age,sep=":"), 1])


# par(mfrow=c(2,1))
# par(mfrow=c(4,5))

for (i in c(1,2,4,5,6,7,8,9,10)){
    ## logistic curve
    plot(NA, ylab="", xlab="", ylim=c(0,0.7), main=gor.names[i])
    
    lines(pred.logit[sim_prop_la$gor==i][order(pred[sim_prop_la$gor==i])], sort(pred[sim_prop_la$gor==i]))
    lines(pred.logit.lowerCI[sim_prop_la$gor==i][order(pred[sim_prop_la$gor==i])], sort(pred[sim_prop_la$gor==i]), col="darkgrey")
    lines(pred.logit.upperCI[sim_prop_la$gor==i][order(pred[sim_prop_la$gor==i])], sort(pred[sim_prop_la$gor==i]), col="darkgrey")
    
    ymin <- par("usr")[3]+0.05; ymax <- par("usr")[4]-0.05
    points(pred.logit.Natsal[Natsal$gor==i],
           (Natsal$cttestly[Natsal$gor==i] * (ymax-ymin)+runif(sum(Natsal$gor==i))/100) + ymin,
           col=rgb(0.1,0.1,0.1,0.5))
    
    # hist(pred.logit.Natsal[Natsal$gor==i & Natsal$cttestly==0], breaks=20, col=rgb(0.1,0.1,0.1,0.5), main="", prob=T, xlim=c(-1,3),ylim=c(0,0.5), xlab="")
    # hist(pred.logit.Natsal[Natsal$gor==i & Natsal$cttestly==1], breaks=10, col=rgb(0.8,0.8,0.8,0.5), add=T, prob=T)
    
    ## densities
    plot(density(pred.logit.Natsal[Natsal$gor==i & Natsal$cttestly==0], prob=T, breaks=30), col="black", type="l", main=gor.names[i], xlim=c(-1,3),ylim=c(0,0.7), xlab="")
    lines(density(pred.logit.Natsal[Natsal$gor==i & Natsal$cttestly==1], breaks=10), col="darkgrey")
}

```

```{r ethnicity_model_validation}

pred.logit <- (fixef(fit)["smokenowTRUE"]*sim_prop_la$smokenow) +
                   fixef(fit)["studentTRUE"]*sim_prop_la$student +
                         ranef(fit)$gor[as.character(sim_prop_la$gor),1] +
               ranef(fit)$'sex:age'[paste(sim_prop_la$sex, sim_prop_la$age,sep=":"), 1]

pred.logit.Natsal <- (fixef(fit)["smokenowTRUE"]*Natsal$smokenow) +
                            fixef(fit)["studentTRUE"]*Natsal$student +
                         ranef(fit)$gor[as.character(Natsal$gor),1] +
                        ranef(fit)$'sex:age'[paste(Natsal$sex, Natsal$age,sep=":"), 1]

# par(mfrow=c(2,1))
# par(mfrow=c(3,4))

for (i in levels(sim_prop_la$ethnic2)[1:6]){
    ## logistic curve
    plot(pred.logit[sim_prop_la$ethnic2==i][order(pred[sim_prop_la$ethnic2==i])], sort(pred[sim_prop_la$ethnic2==i]), type="l", ylab="", xlab="", ylim=c(0,0.65), main=i)
    points(pred.logit.Natsal[Natsal$ethnic2==i], Natsal$cttestly[Natsal$ethnic2==i]*0.6+runif(sum(Natsal$ethnic2==i))/100, col=rgb(0.1,0.1,0.1,0.5))
    
    # hist(pred.logit.Natsal[Natsal$ethnic2==i & Natsal$cttestly==0], breaks=20, col=rgb(0.1,0.1,0.1,0.5), main="", prob=T, xlim=c(-1,3),ylim=c(0,0.5), xlab="")
    # hist(pred.logit.Natsal[Natsal$ethnic2==i & Natsal$cttestly==1], breaks=10, col=rgb(0.8,0.8,0.8,0.5), add=T, prob=T)
    
    ## densities
    plot(density(pred.logit.Natsal[Natsal$ethnic2==i & Natsal$cttestly==0]), col="black", type="l", main=i, xlim=c(0,2.5),ylim=c(0,0.7), xlab="")
    lines(density(pred.logit.Natsal[Natsal$ethnic2==i & Natsal$cttestly==1]), col="darkgrey")
}

```


# Simpler models

##complete pooling
```{r, eval=F}
fit.pool <- lm(formula = cttestly ~ 1,
          data = Natsal, family = binomial(link="logit"))
```


# No pooling: separate estimate within each Region
```{r, eval=F}
fit.gorpool <- list()
for (i in unique(Natsal$gor)){
        fit.gorpool[[i]] <- update(fit.pool, data=Natsal[Natsal$gor==i])

    # fitsep[[i]] <- glmer(formula = cttestly ~ (1|sex)+(1|age)+(1|ethnic2)+smokenow+increasingdrinker+(1|gor),
    #                   data = Natsal[Natsal$gor==1], family = binomial(link="logit"))
}
```


