---
output: word_document
---


```{r}
library(lme4)
library(car)
library(arm)
library(pander)
library(knitr)
library(stargazer)
library(xtable)
library(lattice)

library(STIecoPredict)

load("C:/Users/ngreen1/Dropbox/small-area & chlamydia/R_code/scripts/mrp/data/cleaned-regn-input-mrpNatsal.RData")
```


What are range do we want to regress over? The surveillance data is only for <24 years olds in most cases so theres probably no point in using all ages.

```{r without_region}
# http://stats.stackexchange.com/questions/31569/questions-about-how-random-effects-are-specified-in-lmer

fit0 <- glmer(formula = cttestly ~ 1+(1|age),
              data = Natsal, family = binomial(link="logit"), weights = total_wt)

## a null model
fit12 <- fit0
summary(fit12)

fit13 <- update(fit0, .~. + sex)
summary(fit13)

fit14 <- update(fit13, .~. - (1|age) + (sex|age))
summary(fit14)

fit15 <- update(fit13, .~. + ethnic2)
summary(fit15)

fit16 <- update(fit15, .~. + smokenow+increasingdrinker)
summary(fit16)

fit17 <- update(fit14, .~. + ethnic2+smokenow+increasingdrinker)
summary(fit17)

pander(anova(fit12, fit13, fit14, fit15, fit16, fit17))
```


```{r with_region}

## a null model
fit21 <- glmer(formula = cttestly ~ 1+(1|gor),
              data = Natsal, family = binomial(link="logit"), weights = total_wt)
summary(fit21)

fit22 <- update(fit21, .~. + sex+(1|age))
summary(fit22)

fit23 <- update(fit22, .~. + ethnic2+student)
summary(fit23)

fit24 <- update(fit23, .~. + smokenow+increasingdrinker)
summary(fit24)

fit25 <- update(fit24, .~. - sex - student + sex*student)
summary(fit25)

## random slopes
fit26 <- update(fit25, .~. - (1|age) + (student|age))
summary(fit26)

fit261 <- update(fit25, .~. - (1|age) + (ethnic2|age))
summary(fit261)

## a saturated model
fit27 <- fit26 <- update(fit25, .~. - (1|age) + (student:ethnic2|age))
summary(fit27)

pander(anova(fit21, fit22, fit23, fit24, fit25, fit26, fit261, fit27))

pander(anova(fit12, fit13, fit14, fit15, fit16, fit17, fit21, fit22, fit23, fit24, fit25, fit26, fit261, fit27))
```


```{r}
fitsat <- glmer(formula = cttestly ~ 1+sex+student+smokenow+ (1|age)+(increasingdrinker|ethnic2)+(1|gor),
              data = Natsal, family = binomial(link="logit"), weights = total_wt.int)
                
# save(fitsat, file="C:/Users/nathan.green/Dropbox/small-area & chlamydia/R_code/scripts/mrp/data/fitsat.RData")

fit <- fitsat
# step() doesn't work for random effects models
```


```{r}
fit <- fitsat

# display(fit)

ranef(fit)
se.ranef(fit)
```


```{r}
## prediction plot
model1 <- glmer(cttestly~1+(1|age), binomial, data=Natsal)
xv <- seq(0,45,1)
y <- predict(model1, type="response")
plot(Natsal$age, Natsal$cttestly)
points(Natsal$age, y, col="red")
```

```{r}
## random effects plots
lattice::dotplot(ranef(fitsat, condVar=TRUE))
qqmath(fitsat)
```


```{r try-all-optimisers, eval=FALSE}
# http://stackoverflow.com/questions/23478792/warning-messages-when-trying-to-run-glmer-in-r

aa <- allFit(fit)
is.OK <- sapply(aa,is,"merMod")
## extract just the successful ones
aa.OK <- aa[is.OK]

lapply(aa.OK,function(x) x@optinfo$conv$lme4$messages)  #messages

```


# Append predictions to joint distribution dataset

```{r}

formula <- paste(fit@call$formula, collapse = "")

## convert formula to fixed effect model with same variables
TERMS <- attr(terms(fit@call$formula),"term.labels")
TERMS <- unlist(strsplit(TERMS, split=" \\| "))
TERMS <- gsub(" ", "", TERMS, fixed = TRUE)
TERMS <- TERMS[TERMS!="1" & TERMS!="gor"]

fixeff.formula <- as.formula(paste("cttestly~",paste(TERMS, collapse = "+"),sep=""))

## census data
# test.calcTotalProbs(sim_prop_la)
sim_prop_la <- calcTotalProbs(formula=fixeff.formula, data=sim_prop_la, extracols = c("LAname","gor"))


pred <- invlogit(fixef(fit)["(Intercept)"] +
                     (fixef(fit)["sexWomen"]*(sim_prop_la$sex=="Women")) +
                     (fixef(fit)["studentTRUE"]*sim_prop_la$student) +
                   
                    # if(grep("+ethnic2", formula)==1){}
                     # (fixef(fit)["studentTRUE:sexWomen"]*(sim_prop_la$sex=="Women" & sim_prop_la$student)) +
                     # (fixef(fit)["ethnic2ASIAN/ASIAN BRITISH"]*(sim_prop_la$ethnic2=="ASIAN/ASIAN BRITISH")) +
                     # (fixef(fit)["ethnic2BLACK/BLACK BRITISH"]*(sim_prop_la$ethnic2=="BLACK/BLACK BRITISH")) +
                     # (fixef(fit)["ethnic2CHINESE"]*(sim_prop_la$ethnic2=="CHINESE")) +
                     # (fixef(fit)["ethnic2MIXED"]*(sim_prop_la$ethnic2=="MIXED")) +
                     # (fixef(fit)["ethnic2OTHER"]*(sim_prop_la$ethnic2=="OTHER")) +
                     # (fixef(fit)["ethnic2NOT ANSWERED"]*(sim_prop_la$ethnic2=="NOT ANSWERED")) +
                   
                     (fixef(fit)["smokenowTRUE"]*sim_prop_la$smokenow) +
                     
                    # if(grep("+increasingdrinker", formula)==1){}                     
                     # (fixef(fit)["increasingdrinkerTRUE"]*sim_prop_la$increasingdrinker)+
                     
                   # if(grep("\\(student|age\\)", formula)==1){}
                     # (ranef(fit)$age[as.character(sim_prop_la$age),2]*sim_prop_la$student) +
                   
                   # if(grep("\\(1|ethnic2\\)", formula)==1){}
                      ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),1] +
                   
                   # if(grep("\\(increasingdrinker|ethnic2\\)", formula)==1){}
                      ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),"(Intercept)"] +
                      ranef(fit)$ethnic2[as.character(sim_prop_la$ethnic2),2]*sim_prop_la$increasingdrinker +
    
                   # if(grep("\\(ethnic2|age\\)", formula)==1){}
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "(Intercept)"]) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2ASIAN/ASIAN BRITISH"]*(sim_prop_la$ethnic2=="ASIAN/ASIAN BRITISH")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2BLACK/BLACK BRITISH"]*(sim_prop_la$ethnic2=="BLACK/BLACK BRITISH")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2CHINESE"]*(sim_prop_la$ethnic2=="CHINESE")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2MIXED"]*(sim_prop_la$ethnic2=="MIXED")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2OTHER"]*(sim_prop_la$ethnic2=="OTHER")) +
                     # (ranef(fit)$age[as.character(sim_prop_la$age), "ethnic2NOT ANSWERED"]*(sim_prop_la$ethnic2=="NOT ANSWERED")) +

                   # if(grep("\\(1|age\\)", formula)==1){}
                     ranef(fit)$age[as.character(sim_prop_la$age),1] +
                 
                   # if(grep("\\(1|age.scaled\\)", formula)==1){}
                     # ranef(fit)$age.scaled[as.character(sim_prop_la$age.scaled),1] +
                   
                   # if(grep("\\(1|gor\\)", formula)==1){}
                     ranef(fit)$gor[as.character(sim_prop_la$gor),1]
                   )

predweighted <- pred * sim_prop_la$totalprob
LApred <- tapply(predweighted, sim_prop_la$LAname, sum)
```

The LA specific post-stratified estimates are then
```{r}
as.data.frame(LApred[order(LApred)])
```


# Simpler models

##complete pooling
```{r, eval=F}
fit <- lm(formula = cttestly ~ 1,
          data = Natsal, family = binomial(link="logit"))
```

# No pooling: separate estimate within each Region
```{r, eval=F}
fitsep <- list()
for (i in unique(Natsal$gor)){
        fitsep[[i]] <- update(fit, data=Natsal[Natsal$gor==i])

    # fitsep[[i]] <- glmer(formula = cttestly ~ (1|sex)+(1|age)+(1|ethnic2)+smokenow+increasingdrinker+(1|gor),
    #                   data = Natsal[Natsal$gor==1], family = binomial(link="logit"))
}
```




```{r age-sex_only, eval=F}
pred <- invlogit(fixef(fit)["(Intercept)"] +
                     (fixef(fit)["sexWomen"]*(LApop$sex=="Women")) +
                     ranef(fit)$age[as.character(LApop$age),1]
                   )

predweighted <- pred * LApop$pop.adj
LApred <- tapply(predweighted, LApop$Name, sum)
```

The LA specific post-stratified estimates are then
```{r, eval=F}
as.data.frame(LApred[order(LApred)])
```

